PTWY

### 2023-11-13 Data & Scripts/Old Stats/BOUT.Rmd
Nov. 13
More writing!

```{r Model Labels}
pl<-c(
  '(Intercept)' = "Intercept"
  , BEHAVIORHU = "Behavior"
  , SENTINEL_PRESENCEYES = "Sentinel Presence"
  , 'GENERALIZED_ENVIRONMENTGreen Area' = "Generalized Environment"
  , GROUP_SIZESMALL = "Group Size"
  , BAIT_PRESENCEYES = "Bait Presence"
  , DISTURBANCE_FREQUENCY = "Disturbance Frequency"
  , 'BEHAVIORHU:SENTINEL_PRESENCEYES' = "Behavior: Sentinel Presence"
  , 'BEHAVIORHU:GENERALIZED_ENVIRONMENTGreen Area' = "Behavior: Generalized Environment"
  , 'SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area' = "Sentinel Presence: Generalized Environment"
  , 'BEHAVIORHU:SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area' = "Behavior: Sentinel Presence: Generalized Environment"
)
```

@@

sjPlot::tab_model(BOUT.RMOD2
                  , pred.labels = pl
                  , rm.terms = c("BEHAVIORM"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES"
                                 , "BEHAVIORM:GENERALIZED_ENVIRONMENTGreen Area"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area")
                  , show.re.var = T
                  , title = "Bout Robust Model 2 Output"
                  , dv.labels = " Effects on duration of bouts of behaviors")
```

@@

#### Post Hoc testing

```{r BOUT Post Hoc}
BOUT.DIFF<-emmeans(BOUT.MOD2, ~BEHAVIOR*SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT, pbkrtest.limit = 5070)
test(pairs(BOUT.DIFF, by= "BEHAVIOR"), adjust="fdr")
```
Very cool! These are the results of pairwise comparisons averaged over the levels of group size and bait presence (**Not disturbance frequency**).

@@

However, there are differences in the bout duration of 'head down' behavior. There are differences caused by the presence of a sentinel in commercial areas. There are significant differences between bout durations in commercial areas without a sentinel and bout durations in green areas, in both the presence and absence of a sentinel.

@@

```{r Pairwise comparisons}
BOUT.DOT
```

Huh... I would have expected that there would be significant differences in bouts of 'head up' behavior.

@@

-   Behavior, generalized environment and group size have significant effects. The former is to be expected, while the latter two are interesting, but not very informative (alone).
-   The interaction between behavior and generalized environment are significant. The effect size appears negative for both "head up" and "moving" behavior in green areas.
-   There is a significant interaction of sentinel presence and generalized environment.
-   There is a significant interaction of behavior and group size
-   There is a significant interaction of "moving" and bait presence.

@@

```{r SPxG.ENV BOUT Dot Plot}
SPxG.ENV.DOT<-BOUT %>%
  summarySE(measurevar = "DURATION"
            , groupvars = c("SENTINEL_PRESENCE", "GENERALIZED_ENVIRONMENT")) %>%
    ggplot(aes(x = SENTINEL_PRESENCE
                     , y = DURATION
                     , color = SENTINEL_PRESENCE))+
  geom_point(position = position_dodge(width = 0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(DURATION-se)
                    , ymax=(DURATION+se))
                , width = 0.1
                , position = position_dodge(width=0.9))+
  theme_classic() +
  ylab("Mean Bout Duration (s)") +
  scale_colour_manual(values = cbPalette
                      , guide="none")+
  scale_x_discrete(labels = c("Sentinel Absent", "Sentinel Present"))+
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin()) +
  facet_grid(~GENERALIZED_ENVIRONMENT)

@@

```{r Disturb}
DF.DOT<-BOUT %>%
    ggplot(aes(x = DISTURBANCE_FREQUENCY
               , y = DURATION
               , color = BEHAVIOR))+
  geom_point(size = 3) +
  theme_classic() +
  labs(y="Mean Bout Duration (s)", x="Disturbances per Minute", color= "Behavior")+
  scale_colour_manual(values = cbPalette, labels = c("Foraging", "Alert", "Moving"))+
  scale_x_continuous(n.breaks=14)+
  theme(legend.position = "bottom")

>>>>

```{r Model Labels}
pl<-c(
  '(Intercept)' = "Intercept"
  , BEHAVIORHU = "Behavior"
  , SENTINEL_PRESENCEYES = "Sentinel Presence"
  , 'GENERALIZED_ENVIRONMENTGreen Area' = "Generalized Environment"
  , GROUP_SIZESMALL = "Group Size"
  , BAIT_PRESENCEYES = "Bait Presence"
  , DISTURBANCE_FREQUENCY = "Disturbance Frequency"
  , 'BEHAVIORHU:SENTINEL_PRESENCEYES' = "Behavior: Sentinel Presence"
  , 'BEHAVIORHU:GENERALIZED_ENVIRONMENTGreen Area' = "Behavior: Generalized Environment"
  , 'SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area' = "Sentinel Presence: Generalized Environment"
  , 'BEHAVIORHU:SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area' = "Behavior: Sentinel Presence: Generalized Environment"
)

pl2<-c(
  '(Intercept)' = "Intercept"
  , SENTINEL_PRESENCEYES = "Sentinel Presence"
  , 'GENERALIZED_ENVIRONMENTGreen Area' = "Generalized Environment"
  , GROUP_SIZESMALL = "Group Size"
  , BAIT_PRESENCEYES = "Bait Presence"
  , DISTURBANCE_FREQUENCY = "Disturbance Frequency"
  , 'SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area' = "Sentinel Presence: Generalized Environment"
)
```

@@

sjPlot::tab_model(BOUT.RMOD2
                  , pred.labels = pl
                  , rm.terms = c("BEHAVIORM"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES"
                                 , "BEHAVIORM:GENERALIZED_ENVIRONMENTGreen Area"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area")
                  , show.re.var = T
                  , title = "Bout Robust Model 2 Output"
                  , dv.labels = " Effects on duration of bouts of behaviors")
sjPlot::plot_model(BOUT.RMOD2
                  , axis.labels = pl
                  , rm.terms = c("BEHAVIORM"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES"
                                 , "BEHAVIORM:GENERALIZED_ENVIRONMENTGreen Area"
                                 ,"BEHAVIORM:SENTINEL_PRESENCEYES:GENERALIZED_ENVIRONMENTGreen Area")
                  , show.values=T
                  , show.p=T
                  , value.offset = 0.4
                  , value.size = 3.5
                  , wrap.title = 48
                  , show.re.var = T
                  , title = "Bout Robust Model 2 Output"
                  , dv.labels = " Effects on duration of bouts of behaviors")
```

@@

#### Separate behaviors

I want to determine the effects of my variables within each behavior (excluding 'Moving', since it is not of use to us) to better ascertain the direction of the effects. I will reuse Model 2's formula, removing the behavior from the formula.

```{r BOUT.Mod2 - Separate behavior}
BOUT.MOD2.HD<-rlmer(LDURATION~SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+GROUP_SIZE+BAIT_PRESENCE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = subset(BOUT, BEHAVIOR == "HD"))

BOUT.MOD2.HU<-rlmer(LDURATION~SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+GROUP_SIZE+BAIT_PRESENCE+DISTURBANCE_FREQUENCY+(1|VIDEO_ID/ID), data = subset(BOUT, BEHAVIOR == "HU"))

sjPlot::tab_model(BOUT.MOD2.HD
                  , pred.labels = pl2
                  , show.re.var = T
                  , title = ""
                  , dv.labels = " Effects on duration of bouts with head down")
sjPlot::tab_model(BOUT.MOD2.HU
                  , pred.labels = pl2
                  , show.re.var = T
                  , title = ""
                  , dv.labels = " Effects on duration of bouts with head up")

```

OK! Very interesting! When I separate the behaviors (i.e. not looking at the fixed effects on all behaviors), we get different results.

For head down:
- Sentinel presence is not significant.
- Generalized environment is significant, with increased duration of bouts with head down in green areas.
- Group size is significant, with shorter duration in smaller groups
- The presence of bait increased duration of bouts with head down
- The increased disturbance frequency decreased the duration of bouts with head down
- The interaction between sentinel presence and generalized environment decreased the duration of bouts with head down

For head up:
- All fixed effects not significant
- The interaction between sentinel presence and generalized environment significantly decreased the duration of bouts with head up.

These results differ from those in BOUT.MOD2. This is to be expected since we are now looking at the effects on the separate behaviors.

Let's plot the effect sizes:

```{r Effect sizes - Separate behaviors}
sjPlot::plot_model(BOUT.MOD2.HD
                  , axis.labels = pl2
                  , show.values=T
                  , show.p=T
                  , value.offset = 0.4
                  , value.size = 3.5
                  , wrap.title = 48
                  , show.re.var = T
                  , title = "Effects on head down bout duration")

sjPlot::plot_model(BOUT.MOD2.HU
                  , axis.labels = pl2
                  , show.values=T
                  , show.p=T
                  , value.offset = 0.4
                  , value.size = 3.5
                  , wrap.title = 48
                  , show.re.var = T
                  , title = "Effects on head up bout duration")
```
#### Post Hoc testing

```{r BOUT Post Hoc}
BOUT.DIFF<-emmeans(BOUT.MOD2, ~BEHAVIOR+SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT, pbkrtest.limit = 5070)
test(pairs(BOUT.DIFF, by= "BEHAVIOR"), adjust="fdr")
```
Very cool! These are the results of pairwise comparisons averaged over the levels of group size and bait presence (**Not disturbance frequency**).

@@

However, there are differences in the bout duration of 'head down' behavior. There are differences caused by the presence of a sentinel in commercial areas. There are significant differences between bout duration in commercial areas without a sentinel and bout duration in green areas, in both the presence and absence of a sentinel.

@@

```{r BOUT Dot Plot2}
BOUT.DOT2<-ggplot(data = BOUT.MEAN
               , aes(x = GENERALIZED_ENVIRONMENT
                     , y = DURATION
                     , color = GENERALIZED_ENVIRONMENT
                     , shape = SENTINEL_PRESENCE))+
  geom_point(position = position_dodge(width = 0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(DURATION-se)
                    , ymax=(DURATION+se))
                , width = 0.2
                , position = position_dodge(width=0.9))+
  theme_classic() +
  ylab("Mean Bout Duration (s)") +
  scale_colour_manual(values = cbPalette
                      , guide="none") +
  scale_shape_manual(values = c(16,17)
                     , labels = c("Sentinel Absent"
                                  , "Sentinel Present")
                     , name = "") +
  scale_x_discrete(labels = c("Commercial", "Green Area"))+
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin()) +
  facet_grid(~BEHAVIOR)

BOUT.DOT2
```

@@

-   Behavior, generalized environment and group size have significant effects. The former is to be expected, while the latter two are interesting, but not very informative (alone).

When separating by behavior type, we get more information about the effects of generalized environment and sentinel presence
- Sentinel presence had no effect on the duration of bouts of head down and head up, this is unexpected!
- Generalized environment increased the duration of bout of head down behavior, but not head up. Also unexpected but explainable. Green areas require more time spent with head down to look for and manipulate food, especially when in grass.
- Duration of bouts of head up were not significantly affected by any fixed effects, apart from the interaction between sentinel presence and generalized environment. This decreased the duration of bouts of head up.
- Bouts of head down behavior were also affected by the interaction of sentinel behavior and generalized environment (which decreased the duration), but also group size (smaller = shorter duration), bait presence (yes = shorter duration), and disturbance frequency (higher = shorter duration)

@@

```{r SPxG.ENV BOUT Dot Plot}
SPxG.ENV.DOT<-BOUT %>%
  summarySE(measurevar = "DURATION"
            , groupvars = c("SENTINEL_PRESENCE", "GENERALIZED_ENVIRONMENT", "BEHAVIOR")) %>%
    ggplot(aes(x = SENTINEL_PRESENCE
                     , y = DURATION
                     , color = GENERALIZED_ENVIRONMENT))+
  geom_point(position = position_dodge(width = 0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(DURATION-se)
                    , ymax=(DURATION+se))
                , width = 0.1
                , position = position_dodge(width=0.9))+
  theme_classic() +
  ylab("Mean Bout Duration (s)") +
  scale_colour_manual(values = cbPalette
                      , labels = c("Commercial", "Green")
                      , "Generalized Environment")+
  xlab("Sentinel Presence") +
  scale_x_discrete(labels = c("Absent", "Present")
                   )+
  theme(legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin()) +
  facet_grid(~BEHAVIOR)

@@

```{r Disturb}
DF.DOT<-BOUT[which(BOUT$BEHAVIOR == "HD"),] %>%
    ggplot(aes(x = DISTURBANCE_FREQUENCY
               , y = DURATION
               ))+
  geom_point(size = 2, colour = 'red') +
  theme_classic() +
  labs(y="Mean Head Down Bout Duration (s)", x="Disturbances per Minute")+
  scale_x_continuous(n.breaks=14)+
  theme(legend.position = "bottom")

### 2023-11-13 Data & Scripts/Old Stats/PTWY.Rmd
Nov. 13
More writing!

Seems like it worked. Let's try fitting the model.

@@

```{r MANOVA Vulnerable}
PTWY.vuln<-MANOVA.wide(cbind(PTWY$PTWY_HD.HDP, PTWY$PTWY_HU.HD)~SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT, data = PTWY, subject = "ID.", iter=1000)
summary(PTWY.vuln)
```

@@

```{r PTWY CR Vuln}
simCI(PTWY.vuln, contrast = "pairwise", type = "Tukey", interaction  = F, factor = "GENERALIZED_ENVIRONMENT")

@@

## The other variables

@@

```{r PTWY Vulnerable function}
PTWY.vuln.all<-lapply(PTWY[,c("SENTINEL_PRESENCE"
                              ,"GENERALIZED_ENVIRONMENT"
                              , "GROUP_SIZE"
                              , "BAIT_PRESENCE"
                              , "DISTURBANCE_FREQUENCY")
                              ]
                         , function(x) MANOVA.wide(cbind(PTWY$PTWY_HD.HDP, PTWY$PTWY_HU.HD)~x, data = PTWY, iter = 1000)
                         )
PTWY.SENT<-summary(PTWY.vuln.all$SENTINEL_PRESENCE)
PTWY.GENV<-summary(PTWY.vuln.all$GENERALIZED_ENVIRONMENT)
PTWY.GS<-summary(PTWY.vuln.all$GROUP_SIZE)
PTWY.BP<-summary(PTWY.vuln.all$BAIT_PRESENCE)
PTWY.DF<-summary(PTWY.vuln.all$DISTURBANCE_FREQUENCY)
```

>>>>

Let's try fitting the model.

@@

```{r PTWY MANOVA Vulnerable}
PTWY.vuln<-MANOVA.wide(cbind(PTWY$PTWY_HD.HDP, PTWY$PTWY_HU.HD)~SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT, data = PTWY, subject = "ID.", iter=1000)
summary(PTWY.vuln)
```

@@

```{r PTWY CR Vuln GENV}
simCI(PTWY.vuln, contrast = "pairwise", type = "Tukey", interaction  = F, factor = "GENERALIZED_ENVIRONMENT")

@@

## The other variables - Vulnerability

@@

```{r PTWY Vulnerable function}
PTWY.vuln.all<-lapply(PTWY[,c("SENTINEL_PRESENCE"
                              ,"GENERALIZED_ENVIRONMENT"
                              , "GROUP_SIZE"
                              , "BAIT_PRESENCE"
                              , "DISTURBANCE_FREQUENCY")
                              ]
                         , function(x) MANOVA.wide(cbind(PTWY$PTWY_HD.HDP, PTWY$PTWY_HU.HD)~x, data = PTWY, iter = 1000)
                         )
```
```{r PTWY Vulnerable summaries, echo = F}
PTWY.vuln.SENT<-summary(PTWY.vuln.all$SENTINEL_PRESENCE)
PTWY.vuln.GENV<-summary(PTWY.vuln.all$GENERALIZED_ENVIRONMENT)
PTWY.vuln.GS<-summary(PTWY.vuln.all$GROUP_SIZE)
PTWY.vuln.BP<-summary(PTWY.vuln.all$BAIT_PRESENCE)
PTWY.vuln.DF<-summary(PTWY.vuln.all$DISTURBANCE_FREQUENCY)
```
```{r PTWY Vulnerable Results}
Factor<-c("Sentinel Presence", "Generalized Environment", "Group Size", "Bait Presence", "Disturbance Frequency")
Results.vuln<-cbind(Factor, rbind(PTWY.vuln.SENT, PTWY.vuln.GENV, PTWY.vuln.GS, PTWY.vuln.BP, PTWY.vuln.DF))
Results.vuln
```

As seen above, Gen. env has a  significant effect (p-value = 0.007). Interestingly,  group size (p-value ~ 0.072), bait presence (p-value ~ 0.06), and disturbance frequency (p-value ~ 0.01) are have either significant or marginally significant effects on the frequency of pathways to vulnerability.

### Post Hoc - Disturbance Frequency

```{r PTWY CR Vuln DF}
PTWY.DF.Vuln<-MANOVA.wide(cbind(PTWY$PTWY_HD.HDP, PTWY$PTWY_HU.HD)~DISTURBANCE_FREQUENCY, data = PTWY, iter = 1000)
simCI(PTWY.DF.Vuln, contrast = "pairwise", type = "Tukey", interaction  = F, factor = "DISTURBANCE_FREQUENCY")

HMMMMM... Not significant... Univariate analysis time.

```{r PTWY.DF Vulnerable univar}
PTWY.DF.HD.HDP<-MANOVA.wide(PTWY_HD.HDP~DISTURBANCE_FREQUENCY, data = PTWY, iter = 1000)
PTWY.DF.HU.HD<-MANOVA.wide(PTWY_HU.HD~DISTURBANCE_FREQUENCY, data = PTWY, iter = 1000)

p.adjust(c(PTWY.DF.HD.HDP$resampling[,1], PTWY.DF.HU.HD$resampling[,1]), method = "bonferroni")
#using the parametric bootstrap Wald-type statistic

Curious... the frequency of the pathway HD>HDPeck is marginally significant. Let's quickly plot it.

```{r PTWY.DF.vuln plots}
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
DF.PTWY.vuln<-PTWY %>%
  summarySE(measurevar = "PTWY_HD.HDP"
            , groupvars = "DISTURBANCE_FREQUENCY") %>%
    ggplot(aes(x = DISTURBANCE_FREQUENCY
                     , y = PTWY_HD.HDP
                     , color = DISTURBANCE_FREQUENCY))+
  geom_point(position = position_dodge(width=0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(PTWY_HD.HDP-se)
                    , ymax=(PTWY_HD.HDP+se))
                , width = 0.1
                , position = position_dodge(width=0.9))+
  theme_classic() +
  ylab("Head Down to Head Down + Peck (%)") +
  scale_colour_manual(values = cbPalette
                      , guide="none")+
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin()) +
  scale_x_discrete(limits = c("LOW", "MEDIUM", "HIGH"))

DF.PTWY.vuln

THATS UNEXPECTED... well.. not that unexpected. It mirrors the results of the peck data! As disturbance frequency increases, so does the peck rate, and therefore the frequency of head down to head down + peck. It could be a sense of urgency.

## The other variables - Vulnerability

```{r PTWY Vigilant function}
PTWY.vigil.all<-lapply(PTWY[,c("SENTINEL_PRESENCE"
                              ,"GENERALIZED_ENVIRONMENT"
                              , "GROUP_SIZE"
                              , "BAIT_PRESENCE"
                              , "DISTURBANCE_FREQUENCY")
                              ]
                         , function(x) MANOVA.wide(cbind(PTWY$PTWY_HD.HU, PTWY$PTWY_HDP.HU)~x, data = PTWY, iter = 1000)
                         )
```
```{r PTWY Vigilant summaries, echo = F}
PTWY.vigil.SENT<-summary(PTWY.vigil.all$SENTINEL_PRESENCE)
PTWY.vigil.GENV<-summary(PTWY.vigil.all$GENERALIZED_ENVIRONMENT)
PTWY.vigil.GS<-summary(PTWY.vigil.all$GROUP_SIZE)
PTWY.vigil.BP<-summary(PTWY.vigil.all$BAIT_PRESENCE)
PTWY.vigil.DF<-summary(PTWY.vigil.all$DISTURBANCE_FREQUENCY)
```
```{r PTWY Vigilant Results}
Results.vigil<-cbind(Factor, rbind(PTWY.vigil.SENT, PTWY.vigil.GENV, PTWY.vigil.GS, PTWY.vigil.BP, PTWY.vigil.DF))
Results.vigil
```

Another interesting result! Disturbance frequency is marginally significant for transitions to vigilance. Same workflow as above.

```{r PTWY DF CR Vigil}
PTWY.DF.Vigil<-MANOVA.wide(cbind(PTWY$PTWY_HD.HU, PTWY$PTWY_HDP.HU)~DISTURBANCE_FREQUENCY, data = PTWY, iter = 1000)
simCI(PTWY.DF.Vigil, contrast = "pairwise", type = "Tukey", interaction  = F, factor = "DISTURBANCE_FREQUENCY")

Pairwise comparisons for medium - high is marginally significant.

```{r PTWY.DF Vigil univar}
PTWY.DF.HD.HU<-MANOVA.wide(PTWY_HD.HU~DISTURBANCE_FREQUENCY, data = PTWY, iter = 1000)
PTWY.DF.HDP.HU<-MANOVA.wide(PTWY_HDP.HU~DISTURBANCE_FREQUENCY, data = PTWY, iter = 1000)

p.adjust(c(PTWY.DF.HD.HU$resampling[,1], PTWY.DF.HDP.HU$resampling[,1]), method = "bonferroni")
#using the parametric bootstrap Wald-type statistic

Disturbance frequency has a marginally significant effect on transitions from Head Down + Peck to Head Up. Plot time!

```{r PTWY.DF.vigil plots}
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
DF.PTWY.vigil<-PTWY %>%
  summarySE(measurevar = "PTWY_HDP.HU"
            , groupvars = "DISTURBANCE_FREQUENCY") %>%
    ggplot(aes(x = DISTURBANCE_FREQUENCY
                     , y = PTWY_HDP.HU
                     , color = DISTURBANCE_FREQUENCY))+
  geom_point(position = position_dodge(width=0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(PTWY_HDP.HU-se)
                    , ymax=(PTWY_HDP.HU+se))
                , width = 0.1
                , position = position_dodge(width=0.9))+
  theme_classic() +
  ylab("Head Down + Peck to Head Up  (%)") +
  scale_colour_manual(values = cbPalette
                      , guide="none")+
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin()) +
  scale_x_discrete(limits = c("LOW", "MEDIUM", "HIGH"))

DF.PTWY.vigil

# Frequency

We'll be fitting another manova on the frequency data.

```{r Subsetting FREQ}
FREQ<- PTWY.raw %>%
  dplyr::select(VIDEO_ID.,ID., DECIMAL_TIME, GENERALIZED_ENVIRONMENT, SENTINEL_PRESENCE, BAIT_PRESENCE, NUMBER_OF_CROWS_RECORDED, GROUP_SIZE, TOTAL_FREQUENCY_OF_DISTURBANCES, DISTURBANCE_FREQUENCY | starts_with("FREQ"))

Let's try fitting the model.

```{r FREQ MANOVA Vulnerable}
FREQ.vuln<-MANOVA.wide(cbind(FREQ$FREQ_HD.HDP, FREQ$FREQ_HU.HD)~SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT, data = FREQ, subject = "ID.", iter=1000)
summary(FREQ.vuln)
```

Same as with the PTWY data, only the generalized environment had a significant effect, and that only with the Wald-type statistic. Weird...

```{r FREQ CR Vuln}
simCI(FREQ.vuln, contrast = "pairwise", type = "Tukey", interaction  = F, factor = "GENERALIZED_ENVIRONMENT")

Womp womp. Not significant. :/
However, this still follows the same pattern as the PTWY analysis. Let's perform a univariate analysis to confirm.

```{r FREQ Vulnerable univar}
FREQ.HD.HDP<-MANOVA.wide(FREQ_HD.HDP~GENERALIZED_ENVIRONMENT, data = FREQ, iter = 1000)
FREQ.HU.HD<-MANOVA.wide(FREQ_HU.HD~GENERALIZED_ENVIRONMENT, data = FREQ, iter = 1000)

p.adjust(c(FREQ.HD.HDP$resampling[,1], FREQ.HU.HD$resampling[,1]), method = "bonferroni")
#using the parametric bootstrap Wald-type statistic

Cool! HU>HD is marginally insignificant with a p-value of ~0.08.
Onto vigilance!
